Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-10 sports_analytics.Rmd
final touches

## Example: Win probabilities from betting market data

@@

Many different types of bets can be placed on sports. 
For individual contests, bets involve point spreads, moneylines, odds, or other ways of handicapping which team will win. 
Money can also be wagered on futures, where odds are given in advance for events that may or may not transpire (e.g., a certain team making the playoffs, or a certain player winning the MVP award). 
Here, we focus on betting pools, in which a group of people compete to predict winners in multiple contests (often a tournament), and the inevitable question of whether strategies exist that will consistently beat the market.

>>>>

## Example: Win probabilities from betting market data {#sec:moneylines}

@@

Many different types of bets can be placed on sports. 
For individual contests, bets involve point spreads, moneylines (see Section \ref{sec:moneylines} for an example), odds, or other ways of handicapping which team will win. 
Money can also be wagered on futures, where odds are given in advance for events that may or may not transpire (e.g., a certain team making the playoffs, or a certain player winning the MVP award). 
Here, we focus on betting pools, in which a group of people compete to predict winners in multiple contests (often a tournament).
We also address the inevitable question of whether strategies exist that will consistently beat the market.
